---
title: "Karen Kindaro - Curriculum Vitae"
author: "Karen Kindaro"
output:
  pagedown::html_resume:
    css: ["css/resume.css"]
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = "asis", echo = FALSE,
                      message = FALSE, warning = FALSE)
library(tidyverse)
library(glue)
source("parsing_functions.R")
position_data <- readr::read_csv("positions.csv", show_col_types = FALSE)
PDF_EXPORT <- FALSE
```

Aside
=====================================

Contact
-------------------------------------

- Mesa, Arizona 85201
- +1 208-603-8955
- nangunimba@gmail.com
- [LinkedIn](https://www.linkedin.com/in/8E-250170182/)

Technical Skills
-------------------------------------

```{r skills}
skills <- tibble::tribble(
  ~skill, ~level,
  "Data collection and management", 4,
  "Microsoft Office Suite", 4,
  "Data entry and electronic filing", 5,
  "ETO, Box, and Canvas", 4,
  "R programming and visualization", 3,
  "Excel dashboards and reporting", 4,
  "Digital documentation", 4,
  "Remote collaboration tools", 4,
  "Customer service", 5
)
cat(build_skill_bars(skills), sep = "\n")
```

Languages
-------------------------------------

- Melanesian Pidgin - Native or bilingual
- English - Full professional
- Bislama - Full professional
- Gilbertese - Professional working

Main
=====================================

Karen Kindaro {#title}
-------------------------------------

Detail-oriented Global Management student with strong analytical, research,
and organizational skills. Experienced in data management, technical
problem-solving, and collaborating on team projects. Proficient in Excel and
Google Workspace, with a commitment to accuracy, confidentiality, and
data-driven decision-making.

Work Experience {data-icon=briefcase}
-------------------------------------

```{r experience}
cat(print_section(position_data, "experience"))
```

Education {data-icon=graduation-cap data-concise=true}
-------------------------------------

```{r education}
cat(print_section(position_data, "education"))
```
